Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-22 paper-v1.tex
Gained some lines to keep 12 pages.

Here we describe the main features of Ants-Review.
\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).

\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}). In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback. Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification. An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1  Future developments). It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well. This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.

@@

In the following sections we describe the architecture of the system and its building blocks.
\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h})).
\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d})).
\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})).

@@

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.

\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers by the creation of the community of Anters.
\subsection{Future developments}
An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}. Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) \cite{Wan} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (\emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers for useful comments and revisions.}

>>>>

\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.

@@

\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible. This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).

\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}). In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback. Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification. An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1  Future developments). It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well. This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.

@@

\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h})).
\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d})).
\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})).

@@

\subsubsection{Privacy}
The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.

\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys. However, the privacy is limited by the fact that both the blockchain and its transactions are public.  Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
\paragraph{\textbf{Private transactions}.}AZTEC Protocol  was conceived to enable privacy on public blockchains. It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier. ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.

\subsubsection{Tokenomics}
Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters. zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

\section{Discussions}
We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1). In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers by the creation of the community of Anters.
\subsection{Future developments}
An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}. Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (\emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.

@@

\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the UI/UX.}
